---
title: "Script 6 Boostrap and Friedman.test "
author: "Eziamaka Clinton"
date: "14/11/2019"
output:
  word_document: default
  html_document: default
---
1a.
```{r}
Trades<-c(131,242,24)
Design<-c(204,146,12)
Media<-c(109,51,16)
Other<-c(245,165,18)
obs<-rbind(Trades,Design,Media,Other)
colnames(obs)<-c("Government Loan", "Parents/family/spouse","Other Funding")
rownames(obs)<-c("Trades","Design","Media","Other")
addmargins(obs)
```
b.
$H_0:Canadian\ private\ students'\ fields\ of\ study\ depends\ on\ thier\ major\ source\ of\ funding\ $
$H_a:Canadian\ private\ students'\ fields\ of\ study\ does\ not\ depends\ on\ thier\ major\ source\ of\ funding\ $

c&d.
```{r}
chisq.test(obs) 

#X-squared = 82.63, df = 6, p-value = 1.022e-15
```

e.
After performing our hypothesis test, with a very small p-value of 1.022e-15 which is less than 0.05. So we reject the null hypothesis and conclude that canadian private students' fields of study does not depend on thier major source of funding. 


2.
```{r}
#a.
total<-c(87,105,123)
left<-c(19,40,46)
stayed<-c(total-left)

obs <- matrix(c(left,stayed),c(2,3), byrow = T)
obs

newSum<-addmargins(obs)
newSum1<-prop.table(newSum)
newSum2<-addmargins(newSum1)
colnames(newSum2)<-c("No complaint ","Medical complaint","Non Medical complaint","Sum","Sum")
rownames(newSum2)<-c("Left","Right","Sum","Sum")
newSum2



#b.
leftObsCount<-newSum[1,1:3]
stayObsCount<-newSum[2,1:3]

n<-315

leftexpCount<-c(newSum[1,4]*newSum[3,1]/n,newSum[1,4]*newSum[3,2]/n,newSum[1,4]*newSum[3,3]/n)
stayexpCount<-c(newSum[2,4]*newSum[3,1]/n,newSum[2,4]*newSum[3,2]/n,newSum[2,4]*newSum[3,3]/n)

leftexpCount
stayexpCount

#c.
stat.left<-sum((leftObsCount-leftexpCount)^2/leftexpCount)
stat.stay<-sum((stayObsCount-stayexpCount)^2/stayexpCount)

r.left<-leftObsCount-leftexpCount/sqrt(leftexpCount)
r.stay<-stayObsCount-stayexpCount/sqrt(stayexpCount)

contribution.left<-((r.left)^2/stat.left)*100
contribution.stay<-((r.stay)^2/stat.stay)*100
   
   
```

3.
$H_0:The\ average\ fill\ for\ these\ 4\ machines\ identical$
$H_a:at\ least\ one\ machine\ is\ different$
```{r}
machines1<-c(4.05,4.01,4.02,4.04,3.97)
machines2<-c(3.99,4.02,4.01,3.99,4.00,4.00)
machines3<-c(3.67,3.98,3.97,3.95,4.00)
machines4<-c(4.00,4.02,3.99,4.01,4.03)

machines<-c(machines1,machines2,machines3,machines4)

d1<-rep(1,5)
d2<-rep(2,6)
d3<-rep(3,5)
d4<-rep(4,5)
d<-c(d1,d2,d3,d4)

kruskal.test(machines,d)

#After performing our kruskal test, with a big p-value of 0.03232 which is larger than 0.01. So we fail to reject the null hypothesis.

```

4a.
$H_0:There\ is\ no\ significant\ difference\ in\ tread\ wear$
$H_a:There\ is\ significant\ difference\ in\ tread\ wear$
```{r}
#Blocking Variable: Supplier
#Treatment Variable: Slow, Medium and Fast speeds
#c.The Freidman Test
tires<-c(3.7,3.4,3.5,3.2,3.9,4.5,3.9,4.1,3.5,4.8,3.1,2.8,3.0,2.6,3.4)
group<-rep(1:3, each=5)
blocks<-rep(1:5,3)
tires.out<-data.frame(blocks,group,tires)
tires.out

friedman.test(tires~group|blocks,data = tires.out)

#D. With a smaller p value of 0.006738 which is less than 0.01(significance level), we have to reject the null hyphothesis and conclude that there is indeed significant difference in the tread wear of the tires.
```

5.
```{r}
 boot.funct<-function(B,data){
     n <-length(data)
  theta.b <-c()
  theta.b.star <-c()
  se<-c()
  for(b in 1:B){
    i <-sample(1:n,size=n,replace=T)
    theta.b[b] <-mean(i)
    
    for(b1 in 1:B){
      j <-sample(1:n,size=n,replace=T)
      theta.b.star[b1] <-mean(j)
    }
    se[b] <-sd(theta.b.star)
  }
   z <- (theta.b-mean(theta.b))/se
   z <-sort(z, decreasing = F)
   zR <- z[0.025*length(z)]
   zL <- z[0.975*length(z)]
   
   print(paste("Standard Bootstrap interval:",mean(theta.b)-zL*mean(se),mean(theta.b)-zR*mean(se)))
   theta.b <-sort(theta.b,decreasing = F)
   hat.theta.starL <- theta.b[0.025*length(theta.b)]
   hat.theta.starR <- theta.b[0.975*length(theta.b)]
   
   print(paste("Percentile interval:","(",hat.theta.starL,",", hat.theta.starR,")"))
 }

set.seed(1234)
x <-rnorm(10,0,1)

boot.funct(1000,x)

```