---
title: "Script 4 Summary Statistics"
author: "Eziamaka Clinton"
date: "13/09/2019"
output:
  word_document: default
  html_document: default
---
```{r}

if(!require(Rmisc)){install.packages("Rmisc")}
if(!require(DescTools)){install.packages("DescTools")}
if(!require(plyr)){install.packages("plyr")}
if(!require(boot)){install.packages("boot")}
if(!require(rcompanion)){install.packages("rcompanion")}
```

1.
```{r}

myData <- read.csv("states.csv", header = TRUE)
write.table(myData, "states.txt", row.names = TRUE)
myData2 <- read.table("states.txt")
head(myData2)
```

1i.
```{r}
# Mean, Standard deviation and Summary of the numerical variables.
mean3<-mean(myData2[,3])
median3<-median(myData2[,3])
sd3<-sd(myData2[,3])
summary3<-summary(myData2[,3])
result3.out<-list(mean3, median3, sd3, summary3)
names(result3.out)<-c("Mean", "Median", "SD", "Summary")

mean4<-mean(myData2[,4])
median4<-median(myData2[,4])
sd4<-sd(myData2[,4])
summary4<-summary(myData2[,4])
result4.out<-list(mean4, median4, sd4, summary4)
names(result4.out)<-c("Mean", "Median", "SD", "Summary")

mean5<-mean(myData2[,5])
median5<-median(myData2[,5])
sd5<-sd(myData2[,5])
summary5<-summary(myData2[,5])
result5.out<-list(mean5, median5, sd5, summary5)
names(result5.out)<-c("Mean", "Median", "SD", "Summary")

mean6<-mean(myData2[,6])
median6<-median(myData2[,6])
sd6<-sd(myData2[,6])
summary6<-summary(myData2[,6])
result6.out<-list(mean6, median6, sd6, summary6)
names(result6.out)<-c("Mean", "Median", "SD", "Summary")

mean7<-mean(myData2[,7])
median7<-median(myData2[,7])
sd7<-sd(myData2[,7])
summary7<-summary(myData2[,7])
result7.out<-list(mean7, median7, sd7, summary7)
names(result7.out)<-c("Mean", "Median", "SD", "Summary")

mean8<-mean(myData2[,8])
median8<-median(myData2[,8])
sd8<-sd(myData2[,8])
summary8<-summary(myData2[,8])
result8.out<-list(mean8, median8, sd8, summary8)
names(result8.out)<-c("Mean", "Median", "SD", "Summary")

```

ii.
``` {r}
# 95%CI of all numerical variables
CI(myData2[,3], ci=0.95)
CI(myData2[,4], ci=0.95)
CI(myData2[,5], ci=0.95)
CI(myData2[,6], ci=0.95)
CI(myData2[,7], ci=0.95)
CI(myData2[,8], ci=0.95)
``` 

iii.
The plot is not as informative if all variabes are plotted together. From the seperated plots, we get to have a closer look at the variables with suspected outliers. And also see the variables on thier varying scales. 
```{r}
#Create plot for each numerical variable 

boxplot(myData2[,3], xlab="pop")
boxplot(myData2[,4], xlab="SATV")
boxplot(myData2[,5], xlab="SATM")
boxplot(myData2[,6], xlab="percent")
boxplot(myData2[,7], xlab="dollars")
boxplot(myData2[,8], xlab="pay")

```

iv.
Yes. After plotting of the box, we can notice suspected outlier in some of the variables. The presence of suspected outliers in the pop, dollars, and pay variables.

v. 
Most of the outliers from the varibles were not present in the new plot. Some variables had all their variables removed, while some had the outliers reduced.
```{r}
df<-subset(myData2, select = -c(1,2))

outlierRemover <-function(df) {
  Quantiles <-quantile(df, probs=c(.25, .75))
  Whiskers <- 1.5* IQR(df)
  data.out <- df
  data.out[df<(Quantiles[1]-Whiskers)] <- NA
  data.out[df>(Quantiles[2]+Whiskers)] <- NA
  return(data.out)
}

boxplot(outlierRemover(df[,1]), xlab="pop")
boxplot(outlierRemover(df[,5]), xlab="dollars")
boxplot(outlierRemover(df[,6]), xlab="pay")
```

vi. 
The MTN region had the most regional occurence, PAC and ENC have and equal number of occurence, MA has the least occurence amongst the other variables.
```{r}
#prop.table(df)
prop.region <- table(myData2[,2])/length(myData2[,2])
barchart(prop.region, ylab = "region")
```

2.
```{r}
mySet <- read.table("myData2.txt", header = TRUE)
head(mySet)
```

i.
```{r}
fun.y <- function(a,x){
  y <- a*(x^2)
  return(cbind(x,y))
}

```

ii. 
```{r}
a <- c(-5, -2, 1, 3, 6)
x <- c(mySet[c(1, 2, 3 ,4, 5),1])
y <- fun.y(a,x)


```

iii. Positive linear regression

v.
```{r}
par(mfrow=c(3,3))

qqnorm(y[1,],plot.it = TRUE, main="Y1")
qqline(y[1,], col="blue")

qqnorm(y[2,],plot.it = TRUE,main="Y2")
qqline(y[2,],col="blue")

qqnorm(y[3,],plot.it = TRUE, main="Y3")
qqline(y[3,],col="blue")

qqnorm(y[4,],plot.it = TRUE,main="Y4")
qqline(y[4,],col="blue")

qqnorm(y[5,],plot.it = TRUE,main="Y5")
qqline(y[5,],col="blue")

```

v. After plotting the graphs and seeing the distances from the fittest line of y, we can say the distribution of y was is not normal.
